---
title: "Distribution Types"
author: "PK (Kasidit) Ratanavijai  (Master of Science in Analytics Candidate at The University of Chicago)"
date: "10/4/2019"
output: github_document
---
Note that this are my summarize of Application of Statistic. Hence, it contains my views and comments. "ALL RIGHTS RESERVED"  

## Types of Data  
### **1. Discrete**  
is one that can only take on a finite or countably infinite set of values. Often these values are a subset of the integers such as male vs female, number of coins in a wallet   
**Important discrete distribution to note.**  

1. Unifrom Distribution  
2. Binomial Distribution  
3. Negative Binomial Distribution  
4. Poisson Distribution  

### **2. Continuous**   
can take on all values in some interval such as Height,Time  
**Important continuous distribution to note.**  

1. Exponential Distribution     
2. Normal Distribution  

### Unifrom Distribution  
A discrete uniform distribution describes a random variable that takes on a number
of possible values each with equal probability. For example a coin flip. Its pmf is a
constant (where it is non-zero). A continuous uniform distribution has a pdf that
is constant on some interval.  

**Example exercise**  
Q. Let X be uniform on [0,10]. What is P(X = 7)? What is P(X >7)? What is P(3 ≤ X <7)?  

First, Try to visualize a graph
```{r 1}
uniform = table (runif (100, min = 0 , max = 10))
hist(uniform) 
```

We could also obtain these results using  (). Notice the use of logicals
to restrict the support of the pdf  
```{r}
#What is P(X = 7)? 
dunif(7, max = 10 , min = 0)
# What is P(X >7)? 
punif(7, max = 10 , min = 0, lower.tail = FALSE )
# What is P(3 ≤ X <7)?
punif(7, max = 10 , min = 0, lower.tail = TRUE ) - punif(3, max = 10 , min = 0, lower.tail = TRUE )
```

**Note**  
Although it has a very simple pdf and cdf, the Unif(0, 1) random variable has
several important uses. One such use is related to random number generation. Computers
are not able to generate truly random numbers. Algorithms that attempt to
simulate randomness are called pseudo-random number generators. X ∼ Unif(0, 1)
is a model for an idealized random number generator. Computer scientists compare
the behavior of a pseudo-random number generator with the behavior that would
be expected for X to test the quality of the pseudo-random number generator.  

### Normal Distribution   
The normal distributions form a good model for many numerical populations. Heights, weights, and other physical measurements of organisms often follow an approximately normal distribution.  

In particular, for any normal distribution,  

  * approximately **68%** of the distribution lies within 1 standard deviation of the
mean,
  * approximately **95%** of the distribution lies within 2 standard deviations of the
mean,
  * approximately **99.7%** of the distribution lies within 3 standard deviations of
the mean.

**Example exercise**  
Originally, the mathematics and verbal portions of the Scholastic Aptitude Test
(SAT-M and SAT-V) were normalized based on a sample of 10,000 students who
took the test in 1941. The normalization was designed to give a distribution of
scores that was approximately normal with a mean of 500 and a standard deviation
of 100. Scores were not allowed to exceed 800 or fall below 200, however.
(1) Approximately what percentage of students taking this exam scored between
400 and 700?
(2) Approximately what percentage of students taking this exam scored 800?  

```{r}
#from the premise
u = 500 ; n = 10000 ; sd = 100 ; max. = 800 ; min. = 200
#Q(1)
pnorm(700,mean =500, sd = 100) - pnorm(400,mean =500, sd = 100)
#Q(2)
pnorm(800,mean =500, sd = 100, lower.tail = F) 

```
